Modeling vertical-axis cross-flow turbine wakes

### 2015-07-23 paper.tex
Add array modeling refs
Describe the mesh quantitatively

@@

The computational domain is a rectangular volume
\todo[inline]{Add domain extent in terms of turbine diameter.}
with a cylindrical sliding mesh interface, where the turbine zone rotates at a
mean tip speed ratio $\lambda=1.9$ with a sinusoidal fluctuation at the blade
passage frequency specified to mimic the experimental data. 
\todo[inline]{Get parameters of TSR unsteadiness.}
The 2-D mesh is
shown in Figure~\ref{fig:mesh}.

The mesh topology is kept constant, while its refinement is controlled by a
single parameter---the number of cells in the streamwise direction, $N_x$.

To capture the boundary layer, 20 layers are

In the 3-D mesh, layers are not added to the struts and shaft to save
computational expense.

@@

The 3-D mesh was also generated with \textit{OpenFOAM}'s \textit{snappyHexMesh}
application, with identical domain size, resolution, and boundary layer
parameters in the $x$--$y$ plane, and \todo[inline]{Get $N_z$ for 3-D mesh.}
cells in the vertical direction.

>>>>

Goude and Agren used a 2-D vortex method to simulate a farm of cross-flow
turbines \cite{Goude2010}. Durrani et al. used 2-D CFD to model a group of
cross-flow turbines, but did not compare with experimental results
\cite{Durrani2011}.

@@

The computational domain is a rectangular volume 3.66 m long, 3.66 m wide, and
2.44 m tall (for 3-D), with the turbine located 1.52 m from the inlet, and
centered vertically with a vertical axis. with a cylindrical sliding mesh
interface, where the turbine zone rotates at a mean tip speed ratio
$\lambda=1.9$ with a sinusoidal oscillation at the blade passage
frequency---with and amplitude of 0.19 and the first peak at 0.7 radians---to
mimic the experimental data. The 2-D mesh is shown in Figure~\ref{fig:mesh}.

Meshes were generated using \textit{OpenFOAM}'s \textit{blockMesh} and
\textit{snappHexMesh} utilities. Mesh topology consists of a background
hexahedral mesh, which is refined in all three directions by a factor of 2 in a
rectangular region containing the turbine and near-wake (0.9 m upstream, 1.3 m
downstream and $\pm$ 0.8 m vertically). Cells adjacent to the turbine shaft and
struts are refined by a factor of 4, while cells adjacent to the blades are
refined by a factor of 6. To capture the boundary layer, 20 layers are added
next to the blades with an expansion ratio of 1.2. Overall mesh refinement is
controlled by a single parameter---the number of cells in the streamwise
direction, $N_x$.

@@
